Radioastronomical image reconstruction using Kalman filter under ionospheric perturbations

### 2022-07-28 article/article.tex
update article

	\section{Effects}
	\subsection{Position}
	\subsection{Direction}

>>>>

	\section{Effects of perturbations}

	These perturbations create errors on the matrices used in reconstruction and prediction with Kalman filtering. The goal of this part is to evaluate how much these error affect prediction and reconstruction, to determine if Kalman filtering can be realistically used in radio-astronomic context. \\

	\subsection{Methodology}

	In order to measure precisely the effects, the following methodology will be used :
	\begin{itemize}
		\item 
	\end{itemize}

	\subsection{Position}
	\subsection{Direction}
